Perimeter Control of Swarms

### 2019-01-07 paper.tex
More Updates

\section{Related Work}\label{sec:RelatedWork}
Research has identified several approaches to swarm coordination. Coordination of agent movement was proposed by Reynolds in his "Boid" model in 1987~\cite{REY:87}. This model uses a directional component based on neighbour orientation. The agents communicate with each other to determine a directional vector that is then applied to their movement. This technique has been extended by many authors to incorporate a more strategic advantage in the directional component of the swarms movement. Kawabayashi and Chen proposed an extended model that added predator avoidance and other bounds to make the movement more "organic" but did not add a goal based direction~\cite{KC:08}. Yao and Hwang used GPS signals to identify human movements to be boid-like~\cite{YH:14}. Kovacina et al. took the approach of allowing each agent to select a random direction, which was combined with the orientation of an agents neighbours as a mechanism to move a swarm~\cite{MPYV:02}, this is very similar to how the Boid model functions. The main problem with this approach is that although the swarm is directional there is no destination-based goal.

The closest research to perimeter control, as discussed in this paper, is that of

The technique employed in this paper does not require the identification of the perimeter type as this would require a communications infrastructure.

\section{Baseline specification}
To allow an analysis of each algorithm's effect on a swarm a baseline measurement of `background' variance (jitter) is identified. The baseline measurement provides a comparative data set for the experiments. The baseline data set is for a static swarm (no destination vector) with the same internal parameters.

@@

\section{Destination vector application}
Many mechanisms can be used to influence a swarm to travel in a specific direction. These mechanisms generally involve the use of sensors such as magnetometers or GPS's to achieve a directional coordinate \cite{SG:15,TG:12}.

@@

\section{Swarm destination vector}
The following assumptions are made in this paper:

@@

\section{Identifying the coordinator role}
For an agent to change its role from a standard agent to a coordinator there needs to an algorithm that identifies a set of conditions to trigger the change. This same algorithm also triggers an agent to revert to being a standard agent. The coordinator selection algorithm is separate from the agent coordination algorithms that determine cohesion and repulsion.

@@

\section{Monolithic swarm - (all-agent)} 
In a monolithic swarm \cite{BS:13} the propagation towards the goal is achieved by all the agents using a GPS signal to give each agents' movement a \textit{direction vector} towards a required goal. There is no selection criteria and no computational overhead for the agents.

@@

\section{Simple multifaceted swarm (basic-count)} 
In a simple multifaceted swarm the propagation towards the goal is achieved by generating a \textit{destination vector} for an agent when the agent conforms to a simple counting rule. This \textit{destination vector} is obtained by using the agent's GPS to identify its current coordinate and generating a vector from that coordinate to a specific destination point. This rule creates a subset of agents that apply a local \textit{direction vector} to their movement. This has the effect of creating a directional effect on the whole swarm. The aggregate \textit{direction vector} magnitude of the swarm is less than that produced when all agents apply a \textit{direction vector}. This reduction is further diluted by agents without the \textit{direction vector} calculating a \textit{movement vector} to an equilibrium position. This change in the aggregate \textit{direction vector} will impact on a swarm's `jitter'. This is discussed in more detail in~Section~\ref{sec:AlternateBias1}. With there only being a limited number of peripheral agents invoking their GPS signal there will also be a net reduction in the energy usage of the swarm as discussed in Section~\ref{reduced:EnergyReductionGPS}.

@@

\section{Baseline and effect comparison\label{section:compareBaselineAll1}}
To compare the three algorithms and their effects the metrics applied. The internal movement (jitter), the terminal speed of the centroid of the swarm and the effect on the path of the swarm are considered.

@@

\section{Energy efficiency evaluation}\label{reduced:EnergyReductionGPS}
The effect of an algorithm also effects the amount of gross energy that is used by the swarm in creating the directional effect. If we consider different size physical agents the overall effect of the algorithm can impact on the practical use of the swarm.

@@

\section{Message Propagation Performance}\label{methods:MessagePropogation}
Many algorithms depend upon the propagation of messages throughout a swarm to determine many of the characteristics that allow it to be controlled~\cite{MD:09}. However message propagation has an ($O(n^2)$) propagation profile which effects the speed at which a swarm can react to characteristic changes~\cite{SHA:07}. This could be countered by a reduction in the speed that agents move within a swarm to counter the message propagation delays.

@@

>>>>

The paper is structured as follows: Section~\ref{sec:RelatedWork} discusses related work. Section~\ref{sec:Baseline} introduces a baseline swarm model to allow comparisons of the algorithms presented in this paper. Section~\ref{sec:DestinationApp} discusses th mechanism used to add a directional bias to an agents movement. Section~\ref{sec:CoordRole} discusses the rules by which a coordinator is identified. Section~\ref{sec:AllAgents} discusses the effects of using a GPS directional bias when applied to all the agents. Section~\ref{sec:BasicCount} discusses the application of the basic count algorithm and its effects. Section~\ref{sec:complexMulti}
discusses full perimeter detection and it application. Section~\ref{sec:compareBaselineAll1} compares the effects of the algorithms to the baseline. Section~\ref{sec:EnergyReductionGPS} compares the energy savings of limiting the use of the GPS sensors in coordinating a swarm. Section~\ref{sec:MessagePropogation} discusses the issues associated with message propogation in the identification of perimeter types. Section~\label{sec:conclusion} highlights the findings and Section~\ref{sec:FutureWork} discusses additional applications of the techniques discussed within this paper.

\section{Related Work}\label{sec:RelatedWork}
Research has identified several approaches to swarm coordination. Coordination of agent movement was proposed by Reynolds in his "Boid" model in 1987~\cite{REY:87}. This model uses a directional component based on neighbour orientation. The agents communicate with each other to determine a directional vector that is then applied to their movement. This technique has been extended by many authors to incorporate a more strategic advantage in the directional component of the swarms movement. Kawabayashi and Chen proposed an extended model that added predator avoidance and other bounds to make the movement more `organic' but did not add a goal based direction~\cite{KC:08}. Yao and Hwang used GPS signals to identify human movements to be boid-like~\cite{YH:14}. Kovacina et al. took the approach of allowing each agent to select a random direction, which was combined with the orientation of an agents neighbours as a mechanism to move a swarm~\cite{MPYV:02}, this is very similar to how the Boid model functions. The main problem with these approaches is that although the swarm is directional there is no destination-based goal.

Ant-colony research requires directional agents to implement aforgaing behaviour, the goal is usually to find energy sources and return them to a common base. The initial coordination of the direction of agents in a foraging scenario is randomised. The control component is applied using several different techniques including pheremone trails~\cite{JRD:03,RGJHR:08,VBBLO:15,STZZW:13,SK:16} . Gazi and Passino examined foraging algorithms to measure their stability but the swarms used a random movement approach in the foraging behaviour~\cite{GP:04a}. Hoff et al. used a hybrid approac to their coordination wich does include a directional bias. They achieve this by allowing agents to become beacons~\cite{HSWN:10}. As such they are adding a destination bias to local agent movemnents. However, the mechanism requires local communications and all agents are using a communications infrastructure to identify the beacons. Lee et al. also present a goal-based scenario that utilises GPS however, it is only used by individual agents when returning to a "storehouse"~\cite{LAA:13}.

Alternative approaches also include using a global coordination through unique agent markings and a series of cameras that employ image recognition to coordinate agents to a goal. Furci et al. uses this technique to coordinate crazyfly quadcopters~\cite{FCNSM:15}. This same technique is often used in football playing robots for the `RoboCup' where each team is in effect a swarm~\cite{LL:09}. This technique is shown by Lupashin et al. in their design of a `Flying machine area'~\cite{LSHD:11} and is used by Brescianini et al. when coordinating two quadcopters to pass a pole between each other and balnce it~\cite{BHD:13}. This same technique is also used by Augugliaro et al. to calculate quadcopter trajectories~\cite{ASD:12}.

The use of GPS as a mechanism to coordinate agents within in a swarm is common~\cite{SG:15,TG:12,AZHMJJM:12,MPYV:02,LAA:13,RRSTM:15}. However, the usual approach is to have a directional bias applied to all the agents within the swarm.

The techniques employed in this paper are specifically designed to reduce the utilisation of GPS positioning to a subset of agents within a swarm and does not require the identification of the perimeter type as this would require a communications infrastructure.

\section{Baseline specification}\label{sec:Baseline}
To allow an analysis of each algorithm's effect on a swarm a baseline measurement of `background' variance (jitter) is identified. The baseline measurement provides a comparative data set for the experiments. The baseline data set is for a static swarm (no destination vector) with the same internal parameters.

@@

\section{Destination vector application}\label{sec:DestinationApp}
Many mechanisms can be used to influence a swarm to travel in a specific direction. These mechanisms generally involve the use of sensors such as magnetometers or GPS's to achieve a directional coordinate \cite{SG:15,TG:12}.

@@

%%\section{Swarm destination vector}\label{sec:SwarmDestination}
The following assumptions are made in this paper:

@@

\section{Identifying the coordinator role}\label{sec:CoordRole}
For an agent to change its role from a standard agent to a coordinator there needs to an algorithm that identifies a set of conditions to trigger the change. This same algorithm also triggers an agent to revert to being a standard agent. The coordinator selection algorithm is separate from the agent coordination algorithms that determine cohesion and repulsion.

@@

\section{Monolithic swarm - (all-agent)}\label{sec:AllAgents} 
In a monolithic swarm \cite{BS:13} the propagation towards the goal is achieved by all the agents using a GPS signal to give each agents' movement a \textit{direction vector} towards a required goal. There is no selection criteria and no computational overhead for the agents.

@@

\section{Simple multifaceted swarm (basic-count)}\label{sec:BasicCount} 
In a simple multifaceted swarm the propagation towards the goal is achieved by generating a \textit{destination vector} for an agent when the agent conforms to a simple counting rule. This \textit{destination vector} is obtained by using the agent's GPS to identify its current coordinate and generating a vector from that coordinate to a specific destination point. This rule creates a subset of agents that apply a local \textit{direction vector} to their movement. This has the effect of creating a directional effect on the whole swarm. The aggregate \textit{direction vector} magnitude of the swarm is less than that produced when all agents apply a \textit{direction vector}. This reduction is further diluted by agents without the \textit{direction vector} calculating a \textit{movement vector} to an equilibrium position. This change in the aggregate \textit{direction vector} will impact on a swarm's `jitter'. This is discussed in more detail in~Section~\ref{sec:AlternateBias1}. With there only being a limited number of peripheral agents invoking their GPS signal there will also be a net reduction in the energy usage of the swarm as discussed in Section~\ref{reduced:EnergyReductionGPS}.

@@

\section{Baseline and effect comparison}\label{sec:compareBaselineAll1}
To compare the three algorithms and their effects the metrics applied. The internal movement (jitter), the terminal speed of the centroid of the swarm and the effect on the path of the swarm are considered.

@@

\section{Energy efficiency evaluation}\label{sec:EnergyReductionGPS}
The effect of an algorithm also effects the amount of gross energy that is used by the swarm in creating the directional effect. If we consider different size physical agents the overall effect of the algorithm can impact on the practical use of the swarm.

@@

\section{Message Propagation Performance}\label{sec:MessagePropogation}
Many algorithms depend upon the propagation of messages throughout a swarm to determine many of the characteristics that allow it to be controlled~\cite{MD:09}. However message propagation has an ($O(n^2)$) propagation profile which effects the speed at which a swarm can react to characteristic changes~\cite{SHA:07}. This could be countered by a reduction in the speed that agents move within a swarm to counter the message propagation delays.

@@

\section{Conclusion}\label{sec:conclusion}
\section{Future Work}\label{sec:FutureWork}
